Coherent Hyper-Raman Four Wave Mixing Spectroscopies

### 2024-06-02 paper.tex
Update paper.tex

\section{Experimental Methods}
The ultrafast laser system has been described in detail elsewhere. \cite{RN278, Kaufman2024}
Briefly, an 80 MHz Ti-Sapphire ultrafast oscillator (Spectra-Physics Tsunami) created 35 fs seed pulses, amplified by a 1 kHz regnerative amplifier (Spectra-Physics Spitfire Ace) to approximately 5 W.
A mask in the regenerative amplifier stretched the input pulses to roughly 1 ps.
The resultant output was used to pump four independent OPAs, two of which are relevant for this study.
OPA1 (TOPAS-800, Light Conversion), referred to as $\omega_1$, was tuned for difference frequency generation (DFG) with an external stage (NDFG "DF2", Light Conversion).
OPA2 (OPA-800C, Spectra Physics), referred to as $\omega_2$, was tuned in its signal arrangement. 
Grating and crystal positions in OPA1 was externally controlled using \texttt{WinTOPAS} (Light Conversion).
Grating and BBO crystal positions in OPA2 were computer controlled through communication with 50 mm DC actuators (PMC). %todo: who tf makes PMC motors?
The OPAs were independently tuned through the \texttt{Attune} package, controlled by the \texttt{yaqc} and \texttt{Bluesky} packages. \cite{RN414, RN386, SkyeOPA, KyleOPA}
The power spectra and tuning results are found in Figure X.
Movable retroreflectors (Thorlabs) controlled by 50 mm DC actuators (PMC) are used to measure coherence dynamics.
The beams are focused into the sample using a BOXCARS geometry.\cite{RN308, Kaufman2024}
To enforce frequency dependent temporal pulse overlap, the maximum points of a third order cross correlation between $\omega_1$ and $\omega_3$ measured in CaF$_2$ were used to generate frequency dependent zero delay values.
The nonlinear output was isolated through chopping schemes and a set of spatial apertures, directed into a monochromator (Horiba Micro-HR) and homodyne detected through a photomultiplier tube (Hamamatsu H7422-20), recorded and converted to digital output using a data acquisition unit (National Instruments).
\textit{in-situ} power corrections are performed by dividing the recorded spectra by OPA output measured by home-built pyroelectric detectors.

>>>>

\section{Experimental Methods}
The ultrafast laser system has been described in detail elsewhere. \cite{RN278, Kaufman2024}
Briefly, an 80 MHz Ti-Sapphire ultrafast oscillator (Spectra-Physics Tsunami) created 35 fs seed pulses, amplified by a 1 kHz regnerative amplifier (Spectra-Physics Spitfire Ace) to approximately 0.5 W.
A mask in the regenerative amplifier stretched the input pulses to roughly 1 ps.
The resultant output was used to pump four independent OPAs, two of which are relevant for this study.
OPA1 (TOPAS-800, Light Conversion), referred to as $\omega_1$, was tuned for difference frequency generation (DFG) with an external stage (NDFG "DF2", Light Conversion).
OPA2 (OPA-800C, Spectra Physics), referred to as $\omega_2$, was tuned in its signal arrangement. 
Grating and crystal positions in OPA1 was externally controlled using \texttt{WinTOPAS} (Light Conversion).
Grating and BBO crystal positions in OPA2 were computer controlled through communication with 50 mm DC actuators (PMC). %todo: who tf makes PMC motors?
The OPAs were independently tuned through the \texttt{Attune} package, controlled by the \texttt{yaqc} and \texttt{Bluesky} packages. \cite{RN414, RN386, SkyeOPA, KyleOPA}
The power spectra and tuning results are found in Figure X.%todo: actually graph these
Movable retroreflectors (Thorlabs) controlled by 50 mm DC actuators (PMC) are used to measure coherence dynamics.
The beams are focused into the sample using a BOXCARS geometry.\cite{RN308, Kaufman2024}
To enforce frequency dependent temporal pulse overlap, the maximum points of a third order cross correlation between $\omega_1$ and $\omega_3$ measured in CaF$_2$ were used to generate frequency dependent zero delay values.
The nonlinear output was isolated through chopping schemes and a set of spatial apertures, directed into a monochromator (Horiba Micro-HR) and homodyne detected through a photomultiplier tube (Hamamatsu H7422-20), recorded and converted to digital output using a data acquisition unit (National Instruments).
\textit{in-situ} power corrections are performed by dividing the recorded spectra by OPA output measured by home-built pyroelectric detectors.
